Information Sheet for `Agent Programming in the Cognitive Era' (Viewpoint Paper)

### 2019-10-02 formalisation.tex
cosmetic improvements on ASER grammar

\begin{figure}[htbp]
  \footnotesize{\ttfamily
    \begin{center}
      \begin{tabular}{l c l l} 
   ag & ::= & bs gs gps \\
   bs & ::= & af$_1$ ... af$_{\textrm{n}}$   & (n $\geq$ 0)\\
   gs & ::= & \textbf{!}af$_1$ ... \textbf{!}af$_{\textrm{n}}$ & (n $\geq$ 0)\\
   gps & ::= & gp$_1$ ... gp$_{\textrm{n}}$  & (n $\geq$ 1)\\
   gp & ::= & \textbf{+!}af \textbf{:} lf \textbf{<:} lf \textbf{\{} [
              \textbf{<-} h\textbf{.} ] ( gp \galt op )* \textbf{\}}
              \\ % g-plans 
   op & ::= & te \textbf{:} lf \textbf{<-} h\textbf{.} \\ % old style plans
   te & ::= & \textbf{+}af \galt \textbf{-}af \galt \textbf{+}g  \galt
              \textbf{-}g \\ 
   g  & ::= & \textbf{!}af \galt \textbf{?}af \\
   af & ::= & P\textbf{(}t$_1$\textbf{,} \ldots \textbf{,}
              t$_n$\textbf{)} & (n $\geq$ 0)\\   
   lf & ::= & af \galt $\neg$ lf \galt (lf $\wedge$ lf) \galt (lf $\vee$
              lf) \galt \texttt{true} \\
   h  & ::= & h$_1$\textbf{;} \texttt{true} \galt \texttt{true} \\
   h$_1$ & ::= & a \galt g \galt h$_1$\textbf{;} h$_1$ \\
   a  & ::= & A\textbf{(}t$_1$\textbf{,} \ldots \textbf{,} t$_n$\textbf{)} &  (n $\geq$ 0) \\
\end{tabular}
    \end{center}
}
\caption{Syntax of \aser}
\label{fig:syntax}
\end{figure}

>>>>

\begin{figure}[htbp]
  \footnotesize{\ttfamily
    \begin{center}
      \begin{tabular}{l c l l} 
   ag & ::= & bs gs gps \\
   bs & ::= & af$_{\texttt{1}}$ ... af$_{\texttt{n}}$   & (n $\geq$ 0)\\
   gs & ::= & \textbf{!}af$_{\texttt{1}}$ ... \textbf{!}af$_{\texttt{n}}$ & (n $\geq$ 0)\\
   gps & ::= & gp$_{\texttt{1}}$ ... gp$_{\texttt{n}}$  & (n $\geq$ 1)\\
   gp & ::= & \textbf{+!}af \textbf{:} lf \textbf{<:} lf \textbf{\{} [
              \textbf{<-} h\textbf{.} ] ( gp \galt op )* \textbf{\}}
              \\ % g-plans 
   op & ::= & te \textbf{:} lf \textbf{<-} h\textbf{.} \\ % old style plans
   te & ::= & \textbf{+}af \galt \textbf{-}af \galt \textbf{+}g  \galt
              \textbf{-}g \\ 
   g  & ::= & \textbf{!}af \galt \textbf{?}af \\
   af & ::= & P\textbf{(}t$_{\texttt{1}}$\textbf{,} \ldots \textbf{,}
              t$_{\texttt{n}}$\textbf{)} & (n $\geq$ 0)\\   
   lf & ::= & af \galt $\neg$ lf \galt (lf $\wedge$ lf) \galt (lf $\vee$
              lf) \galt \texttt{true} \\
   h  & ::= & h$_{\texttt{1}}$\textbf{;} \texttt{true} \galt \texttt{true} \\
   h$_{\texttt{1}}$ & ::= & a \galt g \galt h$_{\texttt{1}}$\textbf{;} h$_{\texttt{1}}$ \\
   a  & ::= & A\textbf{(}t$_{\texttt{1}}$\textbf{,} \ldots \textbf{,} t$_{\texttt{n}}$\textbf{)} &  (n $\geq$ 0) \\
\end{tabular}
    \end{center}
}
\caption{Syntax of \aser}
\label{fig:syntax}
\end{figure}
